Thoughts on resubmission within ARC1

### 2009-02-09 doc/client/client_technical.tex
Python broker documentation

Mattias

TODO: finish

>>>>

This broker allows users to write their customized broker in
python. To use this broker the user should write a python class. The
class should contain:

\begin{itemize}

\item{an \_\_init\_\_ method that takes a Config object as input, and}
\item{a SortTargets method that takes a python list of ExecutionTarget
  objects and a JobInnerRepresentation object as input.}

\end{itemize}

The Config, ExecutionTarget and JobInnerRepresentation classes are
available in the swig generated arc python module.

To invoke the python broker, the name of the python module defining
the broker class and the name of the broker class must be given. If
e.g. the broker class MyBroker is defined in the python module
SampleBroker the command line option to arcsub to use this broker is:

\begin{shaded}
\begin{verbatim}
-b PythonBroker:SampleBroker.MyBroker
\end{verbatim}
\end{shaded}

Additional arguments to the python broker can be added by appending
them after an additional colon after the python class name:

\begin{shaded}
\begin{verbatim}
-b PythonBroker:SampleBroker.MyBroker:args
\end{verbatim}
\end{shaded}

Extracting these additional arguments should be done in the python
broker class's \_\_init\_\_ method.

For a complete example of a simple python broker see the
SampleBroker.py file that comes with your arc python installation.
